\documentclass[10.5pt]{article}
\linespread{1.1}

\usepackage{amsfonts,amssymb,amsmath,color,amsthm,abstract}
\usepackage[ps,all,arc,rotate]{xy}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{amscd}
\usepackage{cite}
\usepackage{tikz-cd}
\usepackage[toc,page]{appendix}
\usepackage{hyperref}
\usepackage{tikz}  



\begin{document}
\begin{minipage}{0.5\textwidth}
\noindent{\Large\textbf{Dominic Bunnett}}\\ \\
\end{minipage}
\begin{minipage}{0.5\textwidth}
\noindent Sekretariat MA 3-2\\
Institut f\"ur  Mathematik\\
Straße des 17. Juni 136\\
10623 Berlin, Germany\\
Email: {\em bunnett@math.tu-berlin.de}
%Email : {\em dominic} -dot- {\em bunnett} -at - {\em gmail} -dot- {\em com}\\
%Email: {\em bunnett} -at - {\em math} -dot- {\em tu-berlin} -dot- {\em de}\\
\end{minipage}



\vspace{0.5cm}
\noindent\rule{17cm}{0.4pt}\\
\textbf{\large Education}
\\
\begin{itemize}
\begin{minipage}{0.5\textwidth}
\item {\bf Freie Universit\"at Berlin}\\
{\em Doctor of Philosophy in Mathematics}\\
October 2015-July 2019 .\\
Thesis: Moduli of hypersurfaces in toric \\orbifolds \\ Advisor: Prof. Victoria Hoskins.
\end{minipage}
\begin{minipage}{0.5\textwidth}
\item {\bf University of Warwick}\\ BSc and MMath,  2011-2015, $1^{st}$ class.\\
Thesis: Hodge theory and the Torelli theorem \\for curves\\
Advisor: Prof. Miles Reid.
\end{minipage}


\end{itemize}
\noindent\rule{17cm}{0.4pt}

\noindent\textbf{\large Positions held}\\ \\
$\bullet \,$ {\bf Technische Universit\"at Berlin} \quad  October 2021 - Current\\
Postdoc\\ 
Mentor: Peter B\"urgisser\\ \\
$\bullet \,$ {\bf Makerere University Kampala} \quad April 2022 - January 2023 \\
Lecturer\\ \\
$\bullet \,$ {\bf Technische Universit\"at Berlin} \quad  August 2019 - May 2021\\
Postdoc in Einstein Fellowship\\ 
Mentors: Michael Joswig and Bernd Sturmfels\\ \\
%$\bullet \,$ {\bf Technische Universit\"at Berlin} \quad August 2019 - September 2019\\
%Scholarship of the Einstein Fellowship\\
%Mentor: Bernd Sturmfels\\ \\
$\bullet \,$ {\bf University of Oxford} \quad April - June 2019\\
Visiting Researcher\\
Visiting: Frances Kirwan\\ \\
$\bullet \,$ {\bf Freie Universit\"at Berlin} \quad September 2015 - March 2019\\
Doktorand / Wissenschaftlicher Mitarbeiter\\
Advisor: Victoria Hoskins\\

\noindent\rule{17cm}{0.4pt}\\
\noindent\textbf{Papers}\\
$\bullet \,$ On the moduli of hypersurfaces in toric orbifolds. Proceedings of the Edinburgh Mathematical Society. 2024; 67(2): 577-616.\\
$\bullet \,$ Determinantal representations of the cubic discriminant \em - joint with Hanieh Keneshlou. \em  Le Matematiche, Vol. 75, 2020.\\
$\bullet \,$ Generalised cone complexes and tropical moduli in polymake. {\em joint with Michael Joswig and  Julian Pfeifle.}  In Proceedings of the 2023 International Symposium on Symbolic and Algebraic Computation (ISSAC '23). Association for Computing Machinery, New York, NY, USA, 100–106.\\

\noindent\textbf{Preprints}\\
$\bullet \,$ Moduli of Bridgeland semistable triples {\em joint with Alejandra Rinco-Hidalgo.}\\
$\bullet \,$ Embeddings of weighted projective spaces \em joint with Praise Adeyemo and Fabi\'an Levic\'an-Santib\'a\~nez. \em \href{https://arxiv.org/abs/2510.05076}{arXiv:2510.05076}\\
%$\bullet \,$ Projective moduli of weighted hypersurfaces \em joint with Josh Jackson. \em (in preparation)\\

\noindent\rule{17cm}{0.4pt}\\
\noindent\textbf{Research Visits}\\
$\bullet \,$ Isaac Newton Institute, \emph{New Equivariant Methods in Geometry}, January-June 2024\\
$\bullet \,$ AIMS Rwanda, {\em visiting} Jan Hazla, January 2023\\
$\bullet \,$ Essex Univeristy, Colchester, {\em visiting} Jesus Martinez Garcia, April 2022\\
$\bullet \,$ International Centre of Theoretical Physics, Trieste, {\em visiting} Alejandra Rincon, March 2022\\
$\bullet \,$ University of Oxford,, {\em visiting} Praise Adeyemo and Balázs Szendrői, January 2022 \\
$\bullet \,$ Mathematisches Forschungsinstitut Oberwolfach, Reseach in Pairs, September 2021\\
$\bullet \,$ AIMS Ghana, Guest Lecturer: Introduction to algebraic geometry, Winter Semester 2020\\
%$\bullet \,$ University of Oxford, {\em visiting} Frances Kirwan, April - June 2019\\
$\bullet \,$ International Centre of Theoretical Physics, Trieste, {\em visiting} Tarig Abdelgadir, January 2019\\


\noindent\rule{17cm}{0.4pt}\\
\noindent\textbf{Software} - Available at \url{github.com/dombunnett}\\
$\bullet \,$ Reduced submodules of finite dimensional polynomial modules, \texttt{python}\\
$\bullet \,$ Determinantal representations of the cubic discriminant, \texttt{M2}\\
$\bullet \,$ Automorphism group of a projective toric orbifold, \texttt{polymake}\\
$\bullet \,$ Non-normal simplicies and weighted projective spaces, \texttt{polymake}\\

\noindent\rule{17cm}{0.4pt}\\
\noindent\textbf{Organisational Work}\\
$\bullet \,$ Organiser: Workshop on homological algebra and discrete geometry, Makerere university, Kampala 2021\\
$\bullet \,$ Organiser: Workshop on Nonlinear algebra, TU Berlin, 2020\\
$\bullet \,$ Group Leader: Cubic surfaces workshop, University of Oslo, 2019\\
$\bullet \,$ Facilitator: EAUMP-ICTP Summer school on Homological Methods in Algebra and Geometry, University of Dar-es-Salaam, 2018\\
$\bullet \,$ Organiser: Research seminar - Further topics in geometric invariant theory,  Freie Universit\"at Berlin, Summer Semester 2016\\


\noindent\rule{17cm}{0.4pt}\\
\noindent\textbf{Teaching}\\
$\bullet \,$ Summer Semester 2023, Algebra II (Commutative Algebra), TU Berlin\\
$\bullet \,$ Summer Semester 2022, Algebraic Geometry, Makerere University\\
$\bullet \,$ Winter semester 2021/22, Algebra I (Galois Theory, auf Deutsch), TU Berlin\\
$\bullet \,$ Intro to Homological algebra, December 2021 workshop EAALG\\
$\bullet \,$ Polyhedral geometry and polymake, Abram Gannibal workshop, 2020\\
$\bullet \,$ Summer Semester 2020, Derived categories in algebraic geometry, Makerere University\\
$\bullet \,$ Singularities of affine hypersurfaces, Macaulay2 workshop, 2020\\
$\bullet \,$ Winter semster 2017/18, Linear Algebra I (auf Deutsch), FU Berlin\\
$\bullet \,$ Summer semester 2017, Linear Algebra II (auf Deutsch), FU Berlin\\
$\bullet \,$ Winter semester 2016/17, Differential Geometry I (Berlin mathematics school)\\
$\bullet \,$ Summer of 2014, St. Peters Kubatana High School, Harare, Zimbabwe. Advanced level mathematics\\
$\bullet \,$ 2014-2015, Tutor for undergraduates - analysis, linear algebra, abstract algebra, calculus, Warwick university\\
$\bullet \,$ 2012-2015, Private tutor for a number of A-level and GCSE students, Warwick university\\
\\
\noindent\rule{17cm}{0.4pt}\\
\textbf{Languages}\\
$\bullet \,$English (native)\\
$\bullet \,$German (fluent)\\
%$\bullet \,$French (beginner)\\
$\bullet \,$Lugandan (beginner)
\end{document}
